QALY Comparisons - r`experiment` - r`intervention` - r`baseline`

### 2024-02-27 minos/outcomes/QALY_comparison2.Rmd
Added a generic QALY comparison RNotebook with parameters for the experiment, baseline, and intervention so we can run multiple combinations of these things with the same script

---
title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
params: 
  experiment: experiment 
  baseline: baseline 
  intervention: intervention
  intervention_label: intervention_label
---

@@

@@

```{r read_data, include=False}
experiment <- params$experiment
baseline <- params$baseline
intervention <- params$intervention
intervention_label <- params$intervention_label

out.path <- here::here('output', args$experiment)

@@

combined <- rbind(base, int)
```

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'SF12_uk_scaled')

base.path <- get_latest_runtime_subdirectory(here::here(out.path, 'baseline'))
support.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownlift'))
noSupport.path <- get_latest_runtime_subdirectory(here::here(out.path, 'energyDownliftNoSupport'))

base <- read.csv(paste0(base.path, 'qalys.csv'))
support <- read.csv(paste0(support.path, 'qalys.csv'))
noSupport <- read.csv(paste0(noSupport.path, 'qalys.csv'))

# out.path <- '/home/luke/Documents/WORK/MINOS/PLOTS_FROM_ARC/QALY_TESTING/'
# 
# base <- read.csv(paste0(out.path, 'qalys_baseline.csv'))
# support <- read.csv(paste0(out.path, 'qalys_support.csv'))
# noSupport <- read.csv(paste0(out.path, 'qalys_nosupport.csv'))

# combine the dataframes
combined <- rbind(support, noSupport)
```

@@

combined.diff <- combined %>%
  select(run_id, year, intervention, total_boost) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'total_boost') %>%
  mutate(diff.boost = energyDownlift - energyDownliftNoSupport)

@@

```{r}
auc.plots(base = base,
          base.name = baseline,
          int = int,
          int.name = intervention)
```

@@

```{r}
cost.per.qaly(base = base,
              base.name = baseline,
              int = int,
              int.name = intervention,
              QALY_value = 60000,  # QALY value == £60,000
              int.label <- intervention_label)
```

@@

```{r}
ICER(base = base,
     base.name = baseline,
     int = int,
     int.name = intervention,
     QALY_value = 60000,
     int.label = intervention_label)
```

@@

```{r}
intervention.cost(base = base,
                  base.name = baseline,
                  int = int,
                  int.name = intervention,
                  int.label = intervention_label)
```

```{r}

```

>>>>

---
params:
  experiment: ''
  base: ''
  intervention: ''
title: "QALY Comparisons - r`experiment` - r`intervention` - r`baseline`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

## Parameters

```{r}
# experiment <- params$experiment
# base <- params$base
# intervention <- params$intervention

experiment <- 'default_config'
baseline <- 'baseline'
intervention <- '100All'
```

@@

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', experiment)

@@

# combine the dataframes
combined <- rbind(base, int)
```

@@

combined.diff <- combined %>%
  select(run_id, year, intervention, total_boost) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'total_boost') %>%
  mutate(diff.boost = .data[[intervention]] - .data[[baseline]])

@@

```{r}
auc.plots(base = base, 
          base.name = baseline,
          intervention = int,
          int.name = intervention)
```

@@

```{r}
cost.per.qaly(base = base,
              base.name = baseline,
              int = int,
              int.name = intervention,
              QALY_value = 60000,  # QALY value == £60,000
              int.label <- intervention)
```

@@

```{r}
ICER(base = base,
     base.name = baseline,
     int = int,
     int.name = intervention,
     QALY_value = 60000,
     int.label = intervention)
```

@@

```{r}
intervention.cost(base = base,
                  base.name = baseline,
                  int = int,
                  int.name = intervention,
                  int.label = intervention)
```
